---
title: "assignment2"
author: "CINDY BOSUBEN"
date: '2022-06-20'
output: html_document
---
#This dataset is about thanksgiving for the year 2015,it is stored in a database. It was colllected through a survey called monkeypoll survey where 1058 respondents. It was used to answer here is what Americans eat during thanksgiving. 


```{r setup, include = TRUE}
library(dplyr)
library(knitr)

```

```{r get data, include = TRUE}
#using read.csv to read data from csv file from a URL, 
url <- "https://raw.githubusercontent.com/fivethirtyeight/data/master/thanksgiving-2015/thanksgiving-2015-poll-data.csv"
  
Example<- read.csv(url)

#head(Example, 2)

```

```{r clean data, include = TRUE}
#because there are so many columns, I am going to only pick 5
Example1 <- Example[,c(1,2,3,4,5)]

NewExample<- arrange(Example1, RespondentID)
```
 #This next chunk is inline code
The original dataframe, Example, has `r nrow(Example)`  rows and `r ncol(Example)` columns. The names of the columns and a brief description of each are in the table below:

This makes a new data.frame called text_tbl with two columns, Names and Description
```{r, echo = TRUE}

Names = c("ID", "celebration")
Description = c("RespondentID", "Do you celebrate Thanksgiving") 

text_tbl <- data.frame(Names, Description)

#prints the table

text_tbl

#make the table look pretty
knitr::kable(text_tbl,"pipe")

```

This will subset the data and give me summary stats
```{r, echo = TRUE}
data_pick3 <- select(Example, What.kind.of.stuffing.dressing.do.you.typically.have., What.type.of.cranberry.saucedo.you.typically.have., Do.you.typically.have.gravy.)

Summarytable<-summary(data_pick3)
#creates the summary
Summarytable 
#prints the summary in your output

```



